---
title: "Gillnet Configuration Survey"
author: "Robert Jarrett"
date: "5/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
# load libraries
library(ggplot2)
library(raster)
library(tidyr)
library(sf)
library(dplyr)
library(plotrix)
library(grid)
library(gridExtra)
library(ggpubr)
library(scales)
```

```{r}
#clear environment
rm(list=ls())
```

```{r}
#import data
gillnet.exampledata = read.csv("Data/Example Responses.csv")
# gillnet = gillnet.exampledata
gillnet = read.csv("Data/Cleaned Responses.csv")
statareas = st_read("Stat Area Shapefile/StatAreas.shp")
```

```{r}
#set default theme and colors for plots
theme_set(theme_classic())
update_geom_defaults("boxplot", list(fill = "lightblue2"))
update_geom_defaults("bar", list(fill = "lightblue2", color = "black"))
```

```{r}
#subset survey results to only include current gillnet configurations
current = subset(gillnet, Current.Past == "Current")
```

```{r}
#separate the individual Statistical Areas fished for each respondent
speciessep = separate_rows(current, Species, sep=",")
```

## Fisheries Species
```{r}
#plot a stacked barplot of primary and secondary species
ggplot() +
  stat_count(data=speciessep, aes(x= Species, fill=Configuration), position = 'stack') +
  scale_fill_manual(values=c("firebrick", "lightblue2"))
  labs(title = "Target Species of Primary and Secondary Gillnet Configurations", y = "Number of Fisherman", fill = "Configuration")

#### How to address a fisherman that fishes for the same species in both the primary and secondary configuration
```

## Statisitcal Areas
```{r}
#separate the individual Statistical Areas fished for each respondent
x = separate_rows(current, StatAreas, sep=",")
areaIDs = x$StatAreas
```

```{r}
#calculate count for each Statistical Area fished
countareas = as.data.frame(table(areaIDs))
names(countareas) = c("Id", "count")

#combine the count data and the shapefile
plotareas = merge(statareas, countareas, by.x="Id", all.x = TRUE)
#set NAs to 0
plotareas$count[is.na(plotareas$count)] = 0
```

```{r}
#plot heatmap of statistical areas fished
ggplot() +
  geom_sf(data=plotareas, aes(fill=count)) +
  scale_fill_distiller(direction=1, palette="Reds", aesthetics = "fill") +
  labs(title = "Statisical Areas fished by Survey Respondents", fill = "Number of \nRespondents")

#need to make sure that there aren't any duplicates being plotted across secondary or past configurations
```

## Minimum Depth
```{r}
#plot boxplot of Minimum Depth by Gillnet Type
ggplot() +
  geom_boxplot(data=current, aes(x=GillnetType, y=MinDepth)) +
  labs(title = "Minimum Depth Fished by Gillnet Type", x = "Gillnet Type", y = "Minimum Depth Fished (fathoms)")

#plot boxplot of Minimum Depth by Species
ggplot() +
  geom_boxplot(data=speciessep, aes(x=Species, y=MinDepth)) +
  labs(title = "Minimum Depth Fished by Target Species", x = "Species", y = "Minimum Depth Fished (fathoms)")
```

## Maximum Depth
```{r}
#plot boxplot of Maximum Depth by Gillnet type
ggplot() +
  geom_boxplot(data=current, aes(x=GillnetType, y=MaxDepth)) +
  labs(title = "Maximum Depth Fished by Target Species", x = "Gillnet Type", y = "Maximum Depth Fished (fathoms)")

#plot boxplot of Maximum Depth by Species
ggplot() +
  geom_boxplot(data=speciessep, aes(x=Species, y=MaxDepth)) +
  labs(title = "Maximum Depth Fished by Target Species", x = "Species", y = "Maximum Depth Fished (fathoms)")
```

## Panel Size
```{r}
#plot barplot of Panel Size by Gillnet Type
ggplot(data=current, aes(x=GillnetType, y=PanelSize)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Panel Size by Gillnet Type", x = "Gillnet Type", y = "Panel Size (ft)")

#plot barplot of Panel Size by Species
ggplot(data=speciessep, aes(x=Species, y=PanelSize)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Panel Size by Target Species", x = "Species", y = "Panel Size (ft)")
```

## Number of Panels in a String
```{r}
#plot boxplot of Number of Panels in a String by Gillnet Type
ggplot() +
  geom_boxplot(data=current, aes(x=GillnetType, y=Panels.String)) +
  labs(title = "Number of Panels in a String by Gillnet Type", x = "Species", y = "Number of Panels in a String")

#plot boxplot of Number of Panels in a String by Species
ggplot() +
  geom_boxplot(data=speciessep, aes(x=Species, y=Panels.String)) +
  labs(title = "Number of Panels in a String by Target Species", x = "Species", y = "Number of Panels in a String")
```

## Hanging Height
```{r}
#plot barplot of Hanging Height by Gillnet Type
ggplot(data=current, aes(x=GillnetType, y=HangingHeight)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Hanging Height by Target Species", x = "Species", y = "Hanging Height (fathoms)")

#plot barplot of Hanging Height by Species
ggplot(data=speciessep, aes(x=Species, y=HangingHeight)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Hanging Height by Target Species", x = "Species", y = "Hanging Height (fathoms)")
```

## Splices/Knots
#### Should theses be done as a percentage instead?
```{r}
#plot barplot of Splices/Knots by Gillnet Type
ggplot() +
  geom_bar(data=current, aes(x=Splices.Knots, fill=Splice.KnotType), position="stack") +
  facet_wrap(~GillnetType) +
  labs(title = "Splice vs. Knot Usage by Gillnet Type", x = "Gillnet Type", y = "Number of Fisherman Using", 
       fill = "Splice/Knot Type") +
  scale_fill_brewer(palette = "RdBu") 

#plot barplot of Splices/Knots by Species
ggplot() +
  geom_bar(data=speciessep, aes(x=Splices.Knots, fill=Splice.KnotType), position="stack") +
  facet_wrap(~Species) +
   labs(title = "Splice vs. Knot Usage by Target Species", x = "Species", y = "Number of Fisherman Using", 
        fill = "Splice/Knot Type") +
  scale_fill_brewer(palette = "RdBu") 
```

## Anchors
#### Should theses be done as a percentage instead?
```{r}
#plot barplot of Anchors by Gillnet Type
ggplot() +
  geom_bar(data=current, aes(x=GillnetType, fill=Anchors), position="stack") +
  labs(title = "Anchor Configuration by Gillnet Type", x = "Gillnet Type", y = "Number of Fisherman Using", 
        fill = "Anchor Configuration") +
  scale_fill_brewer(palette = "Blues")

#plot barplot of Anchors by Species
ggplot() +
  geom_bar(data=speciessep, aes(x=Species, fill=Anchors), position="stack") +
  labs(title = "Anchor Configuration by Target Species", x = "Species", y = "Number of Fisherman Using", 
        fill = "Anchor Configuration") +
  scale_fill_brewer(palette = "Blues")
```

## Daytrip/Overnight
#### Should theses be done as a percentage instead?
```{r}
#reorder the Daytrip/Overnight factors
current$Daytrip.Overnight = factor(current$Daytrip.Overnight, levels = c("Daytrip", "Overnight", 'Both'))
speciessep$Daytrip.Overnight = factor(speciessep$Daytrip.Overnight, levels = c("Daytrip", "Overnight", "Both"))
```

```{r}
#plot barplot of Daytrip/Overnight by Gillnet Type
ggplot() +
  geom_bar(data=current, aes(x=Daytrip.Overnight), position=position_dodge()) +
  facet_wrap(~GillnetType) +
  labs(title = "Trip Type by Gillnet Type", x = "Gillnet Type", y = "Number of Fisherman Using")

#plot barplot of Daytrip/Overnight by Species
ggplot() +
  geom_bar(data=speciessep, aes(x=Daytrip.Overnight), position=position_dodge()) +
  facet_wrap(~Species) +
  labs(title = "Trip Type by Target Species", x = "Species", y = "Number of Fisherman Using")
```

## Soak Time
```{r}
#plot barplot of Soak Time by Gillnet Type
ggplot(data=current, aes(x=GillnetType, y=AvgSoakTime)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Average Soak Time by Gillnet Type", x = "Gillnet Type", y = "Average Soak Time (hrs)")

#plot barplot of Soak Time by Species
ggplot(data=speciessep, aes(x=Species, y=AvgSoakTime)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Average Soak Time by Target Species", x = "Species", y = "Average Soak Time (hrs)")
```

## Days per Season
```{r}
#plot barplot of Days per Season by Gillnet Type
ggplot(data=current, aes(x=GillnetType, y=Days.Season)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Days Fished per Season by Gillnet Type", x = "Gillnet Type", y = "Days Fished per Season")

#plot barplot of Days per Season by Species
ggplot(data=speciessep, aes(x=Species, y=Days.Season)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Days Fished per Season by Target Species", x = "Species", y = "Days Fished per Season")
```

## Rope Diameters
```{r}
#create subsetted dataframe for just Rope Diameter data
RopeD = current[c("BuoyLineDiameter", "BridleLineDiameter", "SkirtRopeDiameter", "HeadRopeDiameter", "FootRopeDiameter")]
#take mean and standard error of each rope type
AvgRopeD = apply(RopeD, 2, mean)
SERopeD = apply(RopeD, 2, std.error)
#create vector of rope names for plot
ropenames = c("Buoy Line", "Bridle Line", "Skirt Rope", "Head Rope", "Foot Rope")

#plot barplot of Average Rope Diameter
ggplot(data = NULL, aes(x = ropenames, y = AvgRopeD)) +
  geom_bar(stat = "identity", width = 0.5) +
  geom_errorbar(aes(ymin = AvgRopeD - SERopeD, ymax = AvgRopeD + SERopeD), width = 0.2,) +
  labs(title = "Diameters of Gillnet Rope Types", x = "Rope Type", y = "Rope Diameter (in)")
```

## Buoy Line
```{r}
#plot barplot of Buoy Line Diameter by Gillnet Type
buoyA = ggplot(data=current, aes(x=GillnetType, y=BuoyLineDiameter)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Buoy Line Diameter by Gillnet Type", x = "Gillnet Type", y = "Rope Diameter (in)")
buoyA

#plot barplot of Buoy Line Diameter by Species
buoyB = ggplot(data=speciessep, aes(x=Species, y=BuoyLineDiameter)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Buoy Line Diameter by Target Species", x = "Target Species", y = "Rope Diameter (in)")
buoyB
```

## Bridle Line
```{r}
#plot barplot of Bridle Line Diameter by Gillnet Type
bridleA = ggplot(data=current, aes(x=GillnetType, y=BridleLineDiameter)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Bridle Line Diameter by Gillnet Type", x = "Gillnet Type", y = "Rope Diameter (in)")
bridleA

#plot barplot of Bridle Line Diameter by Species
bridleB = ggplot(data=speciessep, aes(x=Species, y=BridleLineDiameter)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Bridle Line Diameter by Target Species", x = "Target Species", y = "Rope Diameter (in)")
bridleB
```

## Skirt Rope
```{r}
#plot barplot of Skirt Rope Diameter by Gillnet Type
skirtA = ggplot(data=current, aes(x=GillnetType, y=SkirtRopeDiameter)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Skirt Rope Diameter by Gillnet Type", x = "Gillnet Type", y = "Rope Diameter (in)")
skirtA

#plot barplot of Bridle Line Diameter by Species
skirtB = ggplot(data=speciessep, aes(x=Species, y=SkirtRopeDiameter)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Skirt Rope Diameter by Target Species", x = "Target Species", y = "Rope Diameter (in)")
skirtB
```

## Head Rope
```{r}
#plot barplot of Head Rope Diameter by Gillnet Type
headA = ggplot(data=current, aes(x=GillnetType, y=HeadRopeDiameter)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Head Rope Diameter by Gillnet Type", x = "Gillnet Type", y = "Rope Diameter (in)")
headA

#plot barplot of Bridle Line Diameter by Species
headB = ggplot(data=speciessep, aes(x=Species, y=HeadRopeDiameter)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Head Rope Diameter by Target Species", x = "Target Species", y = "Rope Diameter (in)")
headB
```

## Foot Rope
```{r}
#plot barplot of Foot Rope Diameter by Gillnet Type
footA = ggplot(data=current, aes(x=GillnetType, y=FootRopeDiameter)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Foot Rope Diameter by Gillnet Type", x = "Gillnet Type", y = "Rope Diameter (in)")
footA

#plot barplot of Bridle Line Diameter by Species
footB = ggplot(data=speciessep, aes(x=Species, y=FootRopeDiameter)) +
  stat_summary(geom = "bar", fun.y = mean, width = 0.5) +
  stat_summary(geom = "errorbar", fun.data = mean_se, width = 0.25) +
  labs(title = "Foot Rope Diameter by Target Species", x = "Target Species", y = "Rope Diameter (in)") 
footB
```

```{r}
#modify existing Rope Diameter plots to remove axis labels and standardize y axis limits
p1 = buoyA + labs(title = "Buoy Line", x = NULL, y = NULL) + ylim(0, 1)
p2 = bridleA + labs(title = "Bridle Line", x = NULL, y = NULL) + ylim(0, 1)
p3 = skirtA + labs(title = "Skirt Rope", x = NULL, y = NULL) + ylim(0, 1)
p4 = headA + labs(title = "Head Rope", x = NULL, y = NULL) + ylim(0, 1)
p5 = footA + labs(title = "Foot Rope", x = NULL, y = NULL) + ylim(0, 1)

p6 = buoyB + labs(title = "Buoy Line", x = NULL, y = NULL) + ylim(0, 1)
p7 = bridleB + labs(title = "Bridle Line", x = NULL, y = NULL) + ylim(0, 1)
p8 = skirtB + labs(title = "Skirt Rope", x = NULL, y = NULL) + ylim(0, 1)
p9 = headB + labs(title = "Head Rope", x = NULL, y = NULL) + ylim(0, 1)
p10 = footB + labs(title = "Foot Rope", x = NULL, y = NULL) + ylim(0, 1)

#create labels for combined plot
title1 = text_grob("Rope Diameter by Gillnet Type", size = 15, face = "bold")
title2 = text_grob("Rope Diameter by Target Species", size = 15, face = "bold")
bottom1 = text_grob("Gillnet Type", size = 15)
bottom2 = text_grob("Target Species", size = 15)
leftlab = text_grob("Rope Diameter (in)", size = 15, rot = 90)

#plot combined plots for Rope Diameters
grid.arrange(p1, p2, p3, p4, p5,  nrow = 2, top = title1, bottom = bottom1, left = leftlab)
grid.arrange(p6, p7, p8, p9, p10, nrow = 2, top = title2, bottom = bottom2, left = leftlab)
```


















